\begin{frame}
  \frametitle{D3ploy}
  % a comment
  \begin{itemize}
      \item[$\bullet$] A new Cyclus suite was developed for this
                       work. The suite, known as D3ploy, is composed
                       of three new archetypes.
      \item[$\bullet$] A demand driven institution that reacts to 
                       imbalances in demand. This is for situations in
                       which the facilities are being deploy in response
                       to a demand increase.
      \item[$\bullet$] A supply driven institution that reacts to 
                       imbalances in supply. The purpose of this institution
                       is to allow for reactors to drive the deployment
                       of storage facilities, by framing the supply
                       of spent fuel as a demand for storage space. 
      \item[$\bullet$] A deterministic institution that solves a matrix
                       equation to deploy facilities. The matrix is fix
                       at the start of the simulation.

   \end{itemize}        
\end{frame}

\begin{frame}
  \frametitle{Testing Automated Deployment of Support Facilities}
  % a comment
  \begin{itemize}
      \item[$\bullet$] The first test looks at the deployment of support
                       facilties for reactors. 
      \item[$\bullet$] In this test reactors will be deployed to met a linear
                       growth rate of 3 reactors per year. 
      \item[$\bullet$] Each reactor requires a source facility to supply it
                       per year, therefore there should be a similar growth
                       in these facilties with comparison to reactors. 
   \end{itemize}        
\end{frame}

\begin{frame}
  \frametitle{Results from Simple Fuel Cycle Test - Power}
        \begin{tabular}{c c c}
        Method & Number of Time Undersupplyied & Total Undersupply \\
        MA & 82 & 1074 \\
        ARMA& 70 & 244 \\
        ARCH & 88 & 981 \\
        FFT & 26 & 63 \\
        Exp-Smoothing & 65 & 457 \\
        Holt-Winters & 65 & 457 \\
        Seasonal & 3 & 8 \\
        Poly & 55 & 336
        \end{tabular}
\end{frame}

\begin{frame}
  \frametitle{Github Statistics}
  % slide about the github statistics of the project.
    \item[$\bullet$] Over the course of the project, the software was 
                    managed using Github.
    \item[$\bullet$] Over the three years, there have been 170 crucial
                     issues created, and closed for the software. 
    \item[$\bullet$] In addition to the D3ploy software creation there
                     have been 9 software updates to the Cycamore software,
                     and 12 updates to the Cyclus software.             
\end{frame}
