\begin{frame}
  \frametitle{Goal of the Project}
  % a comment
  \begin{itemize}
      \item[$\bullet$] The primary goal of the project was to upgrade the Cyclus Fuel Cycle
                       Simulator to include the capability to automatically deploy fuel
                       cycle facilities for the user.
      \item[$\bullet$] This functionality would be added to a Cyclus Institution class agent.
      \item[$\bullet$] The automated deployment would be managed using time series algorithms
                       to predict the value of future timesteps based on previous data.
   \end{itemize}        
\end{frame}

\begin{frame}
  \frametitle{Goal of the Project}
  % a comment
  \begin{itemize}
    \item[$\bullet$] Three types of methods were looked at for doing the prediction.
    \item[$\bullet$] Non-optimizing methods. These methods included moving average
                     , autoregressive moving average (ARMA), and autoregressive
                     heteroskidasticity (ARCH) models. 
    \item[$\bullet$] Deterministic models. These models use a methodology that will
                     always return the same answer given a unique input. This includes
                     Fast Fourier Transforms, Exponential Smoothing, Holt-Winters,
                     Polynomial regression. 
    \item[$\bullet$] Stochastic models. With stochastic models, the output is based
                     on randomly sampling models to determine the behavior of the 
                     next time step. The method implimented here is a machine learning
                     seasonal method. 
   \end{itemize}        
\end{frame}

\begin{frame}
  \frametitle{Why Automate Fuel Cycle Deployment?}
  % a comment
  \begin{itemize}
      \item[$\bullet$] Automating deployments to meet power demands can be difficult for complicated
                       transition scenarios. 
      \item[$\bullet$] The deployment of reactors to create a balanced closed fuel cycle can be a 
                       complicated process. Ensuring that there is enough fast reactor fuel for
                       their operation requires the appropriate support fleet of light water reactors.
      \item[$\bullet$] Additionally, requiring users figure out the correct number of support
                       structures for the reactors fleets is a tedious job for humans.
   \end{itemize}        
\end{frame}
